Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-07-29 tex/ms.tex
add note about SED tension
adding references

% ---- Charlie (emulateapj) mode ----
 \documentclass[iop,numberedappendix]{emulateapj}
 \usepackage{apjfonts}
% ----
\usepackage{color}
\bibliographystyle{apj}
\input{vc}

@@

@@

The data we use to test our method consist of optical spectroscopy of
XX stellar clusters in M31 for which YY-band HST photometric data
exist.  The optical spectra were obtained using the fiber-fed
Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
of the spectra is $3700-9100 \AA$. The instrumental resolution is
$\sim 5\AA$ across the optical range \citep{fabricant13}.  {\color{blue} Wavelength
calibration happened. Sky subtraction happened.} The data were
approximately spectrophotometrically calibrated using an average
calibration vector for the night constructed from {\color{blue} MORE
HERE. Discuss S/N, sky subtraction.}

An example spectrum, both after and before spectrophotometric
calibration, is shown in Figure \ref{fig:data}.  When fitting the
spectra we mask the region around the bright OI5577 sky line, and we
fit only to the spectrum with $3750 < \lambda < 7200$ to avoid the low
S/N edges and, on the red side, imperfect sky line subtraction in a
region of the spectrum that has a paucity of informative spectral
lines. Furthermore, the MILES spectral library (see
\S\ref{sec:cluster_model}) only extends to $\lambda < 7500$\AA.
{\color{red} Specify/Justify order of calibration polynomial here?}.

@@

The spectrum of one solar mass of stars that formed at lookback time
$t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$.
Here the additional parameters $\beta$ may include details of the
population synthesis model, such as the IMF slope and adjustments to
the stellar spectra or stellar evolutionary tracks. We will assume
$\beta$ to be fixed for the purposes of this exercise, with no loss of
generality {\color{blue} (KEEPING IMF SLOPE CONSTANT)}.  We will also fix the
shape of the attenuation curve, $k_\lambda \equiv
\tau_\lambda/\tau_V$, to the Milky way average of \citet{CCM89} with
$R_V=3.1$ and assume that $d_L$ is known to high precision from
independent methods and can therefore be treated as fixed.  In
practice, $d_L$ is completely degenerate with $m_*$. We calculate
$S(\lambda, t, Z)$ using the Flexible Stellar Population Synthesis
code \citep[FSPS][]{FSPS}.  We use the Padova isochrones
\citep{Padova} and the MILES stellar spectral library \citep{MILES}.

@@

The final mean model is then given by 
\begin{eqnarray}\label{eq:MeanModel} 
\mu(\theta) &  = & (G_\sigma  \otimes F_{\theta^\prime})(\lambda) +
\sum_{\ell=0}^{N_\ell} S_\ell \\
S_\ell & = & \frac{A_\ell}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda -
 \lambda_\ell)^2}{2\sigma_e^2})\\
\theta & \equiv & \left[ \{\theta^\prime\}, \sigma, \{A_\ell\}_{\ell=0}^{N_l},
  \sigma_e \right]
\quad ,
\end{eqnarray}
where $G_\sigma$ represents a Gaussian of unit area 
and standard deviation $\sigma$, 
$\otimes$ indicates convolution, 
and the full parameter set $\theta$ now includes
the instrumental wavelength broadening $\sigma$ 
and the dispersion $\sigma_e$ and
amplitudes $A_\ell$ of the $N_l$ nebular emission and interstellar
absorption lines.
This is the mean model which appears in equation
\ref{eq:SpectroscopicLF}.

@@

We estimate the posterior through MCMC sampling after an initial round
of optimization using Powell's method.  The specific sampling
algorithm we use is the affine-invariant ensemble sampling scheme of
\citet{GW}, as implemented in the \texttt{emcee} package \cite{dfm}
Unlike typical Metropolis-Hastings MCMC sampling, the affine-invariant
sampler does not require the specification of step sizes in each
dimension.  {\color{blue}ASSESSING SAMPLER CONVERGENCE}

@@

In Figure \ref{fig:inferred_sed} we show the corresponding SED for the
posterior parameter draws, compared to the observed SED. Finally, In
Figure \ref{fig:inferred_params} we show the marginalized and joint
PDFs for a subset of the full model parameters.

@@

The physical model parameters that we infer indicate that \excluster~
has super-solar metallicity, an age of $\sim 225$ Myr, moderate dust
extinction, and a stellar mass of $\sim 10^{4}$ M$_{sun}$ {\color{blue}
check that this is current mass, not initial mass}.  We find a spectral
broadening of $\sim 1.75$\AA (4.1\AA FWHM), which when combined in
quadrature with the intrinsic resolution of the MILES library, 2.5\AA
FWHM \citep{beifiori11}, reproduces the typical line-spread function
of the MMT Hectospec instrument, $\sim 5.0$\AA \citep{fabricant13}.
We obtain strong constraints on the systemic velocity.

@@

\acknowledgements
Thanks to X. for bringing us beer.
DRW is supported by NASA through Hubble Fellowship grant
  HST-HF-51331.01 awarded by the Space Telescope Science Institute.
BDJ and DRW acknowledge the hospitality of Hans-Walter Rix and the MPIA. 
CC is supported by Packard and Sloan Foundation Fellowships. 
This research made extensive use of NASA's Astrophysics Data System Bibliographic Services. 
In large part, analysis and plots presented in this paper utilized
  iPython and packages from NumPy, SciPy, and Matplotlib
  \citep[][]{hunter2007, oliphant2007, perez2007, astropy2013} as well
  as python-FSPS  (http:://github.com/dfm/python-fsps) .

>>>>

% ---- Charlie (emulateapj) mode ----
 \documentclass[iop,numberedappendix]{emulateapj}
 \usepackage{apjfonts}
% ----
\usepackage{color, hyperref}
\bibliographystyle{apj}
\input{vc}

@@

%references
\newcommand{\foreign}[1]{\emph{#1}}
\newcommand{\etal}{\foreign{et\,al.}}

@@

The data we use to test our method consist of optical spectroscopy of
XX stellar clusters in M31 for which YY-band HST photometric data
exist.  The optical spectra were obtained using the fiber-fed
Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
of the spectra is $3700-9100$\AA. The instrumental resolution is
$\sim 5$\AA~ across the optical range \citep{fabricant13}.  {\color{blue} Wavelength
calibration happened. Sky subtraction happened.} The data were
approximately spectrophotometrically calibrated using an average
calibration vector for the night constructed from {\color{blue} MORE
HERE. Discuss S/N, sky subtraction.}

An example spectrum, both after and before spectrophotometric
calibration, is shown in Figure \ref{fig:data}.  When fitting the
spectra we mask the region around the bright OI5577 sky line, and we
fit only to the spectrum with $3750 < \lambda < 7200$\AA~ to avoid the low
S/N edges and, on the red side, imperfect sky line subtraction in a
region of the spectrum that has a paucity of informative spectral
lines. Furthermore, the MILES spectral library (see
\S\ref{sec:cluster_model}) only extends to $\lambda < 7500$\AA.
{\color{red} Specify/Justify order of calibration polynomial here?}.

@@

The spectrum of one solar mass of stars that formed at lookback time
$t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$.
Here the additional parameters $\beta$ may include details of the
population synthesis model, such as the IMF slope and adjustments to
the stellar spectra or stellar evolutionary tracks. We will assume
$\beta$ to be fixed for the purposes of this exercise, with no loss of
generality {\color{blue} (KEEPING IMF SLOPE CONSTANT)}.  We will also
fix the shape of the attenuation curve, $k_\lambda \equiv
\tau_\lambda/\tau_V$, to the Milky way average of \citet{CCM89} with
$R_V=3.1$ and assume that $d_L$ is known to high precision from
independent methods and can therefore be treated as fixed.  In
practice, $d_L$ is completely degenerate with $m_*$. We calculate
$S(\lambda, t, Z)$ using the Flexible Stellar Population Synthesis
code \citep[FSPS][]{fsps}.  We use the Padova 2007 isochrones
\citep{girardi00, bertilli94, marigo07} and the MILES stellar spectral
library \citep{miles_I, miles_II, miles_III}.

@@

The final mean model is then given by 
\begin{eqnarray}\label{eq:MeanModel} 
\mu(\theta) &  = & (G_\sigma  \otimes F_{\theta^\prime})(\lambda) +
\sum_{\ell=0}^{N_\ell} S_\ell \\
S_\ell & = & \frac{A_\ell}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda -
 \lambda_\ell)^2}{2\sigma_e^2})\\
\theta & \equiv & \left[ \{\theta^\prime\}, \sigma, \{A_\ell\}_{\ell=0}^{N_l},
  \sigma_e \right]
\quad ,
\end{eqnarray}
where $G_\sigma$ represents a Gaussian of unit area 
and standard deviation $\sigma$, 
$\otimes$ indicates convolution, 
and the full parameter set $\theta$ now includes
the instrumental wavelength broadening $\sigma$ 
and the dispersion $\sigma_e$ and
amplitudes $A_\ell$ of the $N_l$ nebular emission and interstellar
absorption lines.
This is the mean model which appears in equation
\ref{eq:spectroscopicLF}.

@@

We estimate the posterior through MCMC sampling after an initial round
of optimization using Powell's method.  The specific sampling
algorithm we use is the affine-invariant ensemble sampling scheme of
\citet{goodman}, as implemented in the \texttt{emcee} package \citep{emcee}
Unlike typical Metropolis-Hastings MCMC sampling, the affine-invariant
sampler does not require the specification of step sizes in each
dimension.  {\color{blue}ASSESSING SAMPLER CONVERGENCE}

@@

In Figure \ref{fig:inferred_sed} we show the corresponding SED for the
posterior parameter draws, compared to the observed SED. There is some
tension between the modeled and observed SEDs, I'm not quite sure
why. Finally, In Figure \ref{fig:inferred_params} we show the
marginalized and joint PDFs for a subset of the full model parameters.

@@

The physical model parameters that we infer indicate that \excluster~
has super-solar metallicity, an age of $\sim 225$ Myr, moderate dust
extinction, and a stellar mass of $\sim 10^{4}$ M$_{sun}$ {\color{blue}
check that this is current mass, not initial mass}.  We find a spectral
broadening of $\sim 1.75$\AA~ (4.1\AA~ FWHM), which when combined in
quadrature with the intrinsic resolution of the MILES library, 2.5\AA~
FWHM \citep{beifiori11}, reproduces the typical line-spread function
of the MMT Hectospec instrument, $\sim 5$\AA~ \citep{fabricant13}.
We obtain strong constraints on the systemic velocity.

@@

\acknowledgements
Thanks to X. for bringing us beer.
DRW is supported by NASA through Hubble Fellowship grant
  HST-HF-51331.01 awarded by the Space Telescope Science Institute.
BDJ and DRW acknowledge the hospitality of Hans-Walter Rix and the MPIA. 
CC is supported by Packard and Sloan Foundation Fellowships. 
This research made extensive use of NASA's Astrophysics Data System Bibliographic Services. 
In large part, analysis and plots presented in this paper utilized
  iPython and packages from NumPy, SciPy, and Matplotlib
  \citep[][]{hunter2007, oliphant2007, perez2007} as well
  as python-FSPS  (\url{http:://github.com/dfm/python-fsps}) .

\newcommand{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{arXiv:#1}}
\begin{thebibliography}{}\raggedright

\bibitem[Beifiori \etal(2011)]{beifiori11} 
Beifiori, A., Maraston, C., Thomas, D., \& Johansson, J.\ 2011, \aap, 531, A109

\bibitem[Bertelli et al.(1994)]{bertelli94} Bertelli, G., Bressan, A., Chiosi, C., Fagotto, F., \& Nasi, E.\ 1994, \aaps, 106, 275

\bibitem[Cardelli \etal(1989)]{CCM89} 
Cardelli, J.~A., Clayton, G.~C., \& Mathis, J.~S.\ 1989, \apj, 345, 245

\bibitem[Cenarro \etal(2007)]{miles_II} 
Cenarro, A.~J., Peletier, R.~F., S{\'a}nchez-Bl{\'a}zquez, P., et al.\ 2007, \mnras, 374, 
664

\bibitem[Conroy \etal(2009)]{fsps} 
Conroy, C., Gunn, J.~E., \& White, M.\ 2009, \apj, 699, 486

\bibitem[Conroy \& Gunn(2010)]{fsps_cal} 
Conroy, C., \& Gunn, J.~E.\ 2010, \apj, 712, 833

\bibitem[Fabricant \etal(2013)]{fabricant13} 
Fabricant, D., Chilingarian, I., Hwang, H.~S., et al.\ 2013, \pasp, 125, 1362

\bibitem[Falc{\'o}n-Barroso \etal(2011)]{miles_III} 
Falc{\'o}n-Barroso, J., S{\'a}nchez-Bl{\'a}zquez, P., Vazdekis, A., et al.\ 2011, \aap, 532, A95

\bibitem[Foreman-Mackey \etal(2012)]{emcee}
Foreman-Mackey, D., Hogg, D.~W., Lang, D., \& Goodman, J.\ 2013, \pasp, 125,
306 (\arxiv{1202.3665})

\bibitem[Girardi et al.(2000)]{girardi00} 
Girardi, L., Bressan, A., Bertelli, G., \& Chiosi, C.\ 2000, \aaps, 141, 371

\bibitem[Goodman~\&\ Weare(2010)]{goodman}
Goodman,~J. \& Weare,\ J., 2010, Comm.\ App.\ Math.\ Comp.\ Sci., 5, 65

\bibitem[Marigo \& Girardi(2007)]{marigo07} 
Marigo, P., \& Girardi, L.\ 2007, \aap, 469, 239

\bibitem[S{\'a}nchez-Bl{\'a}zquez \etal(2006)]{miles_I} 
S{\'a}nchez-Bl{\'a}zquez, P., Peletier, R.~F., Jim{\'e}nez-Vicente,
J., et  al.\ 2006, \mnras, 371, 703

\end{thebibliography}
